---
title: "Extracting Function Words of Interest from Childes - French"
author: "Samantha Bai"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(childesr)
library(tidyverse)
library(arrow)
library(stringr)
library(dplyr)
library(knitr)
```

# Loading Data from Childes-DB

We use the package `childesr` to access the data in the CHILDES database. The
code below downloads and stores all utterances by children and parents from the
French collection. Unlike Mandarin (where we selected specific corpora out of
the Chinese collection), the `French` collection maps cleanly to the language,
so we pull the whole collection.

```{r french_collection}
target_collection <- "French"
```

```{r directories}
# Create directories
dir.create("../french/french_data/raw_data", showWarnings = FALSE, recursive = TRUE)
dir.create("../french/french_data/processed_data", showWarnings = FALSE, recursive = TRUE)
```

```{r ChildesDBimports}
# Define file paths
feather_path <- "../french/french_data/raw_data/all_french_tokens.feather"
csv_path <- "../french/french_data/raw_data/all_french_tokens.csv"

if (file.exists(feather_path)) {
  cat("existing data found\n")
  cat(sprintf("Found existing data file: %s\n", feather_path))
  cat("Loading from saved feather file...\n\n")

  all_french_tokens <- arrow::read_feather(feather_path)

} else if (file.exists(csv_path)) {
  cat("existing csv data found\n")
  cat(sprintf("Found existing data file: %s\n", csv_path))
  cat("Loading from CSV file...\n\n")

  all_french_tokens <- readr::read_csv(csv_path, show_col_types = FALSE)

  cat("Saving feather version for faster future loading...\n")
  arrow::write_feather(all_french_tokens, feather_path)

} else {
  cat("No existing data found - downloading from Childes\n")

  all_french_tokens <- get_tokens(
    collection = target_collection,
    role = c("Target_Child", "Mother", "Father"),
    token = "*"
  )

  cat("Saving downloaded data...\n")
  arrow::write_feather(all_french_tokens, feather_path)
  readr::write_csv(all_french_tokens, csv_path)
}

cat(sprintf("Loaded %d tokens from %d children\n",
            nrow(all_french_tokens),
            dplyr::n_distinct(all_french_tokens$target_child_id)))
```

# Token Processing

## Exclusions

The following script cleans up the data. Unlike Mandarin, French has case, so we
lowercase the gloss for consistent matching. We exclude tokens with missing age
and those above 72 months of the child's age. All exclusions are stored in a
file called exclusions_french_summary.csv

```{r exclusionsTokens}
# French has case distinctions, so normalise gloss to lowercase
all_french_tokens$gloss <- tolower(all_french_tokens$gloss)

# Count tokens before exclusions
n_tokens_before_exclusions <- nrow(all_french_tokens)

# Number of children before exclusions
n_chi_before_exclusions <-
  all_french_tokens$target_child_id %>% unique() %>% length()

french_tokens <- all_french_tokens

# Removing rows for which age information for the child does not exist
french_tokens <-
  french_tokens %>% drop_na(target_child_age)

# Count the tokens after removing NA tokens
n_tokens_ageNAs_removed <- nrow(french_tokens)

# Number of children after excluding NAs
n_chi_ageNAs_removed <-
  french_tokens$target_child_id %>% unique() %>% length()

# Take out data for the age range above 6 years (72 months)
french_tokens <-
  french_tokens %>%
  filter(target_child_age < 72)

# Count the tokens after excluding older than 6 age range
n_tokens_ageOver72mo_removed <- nrow(french_tokens)

# Number of children left after exclusions
n_chi_ageOver72mo_removed <-
  french_tokens$target_child_id %>% unique() %>% length()

# Record the dataframe of exclusions
exclusions <-
  data.frame(
    n_tokens_before_exclusions = n_tokens_before_exclusions,
    n_after_ageNAs = n_tokens_ageNAs_removed,
    n_after_age72mo = n_tokens_ageOver72mo_removed,
    missing_age = n_tokens_before_exclusions - n_tokens_ageNAs_removed,
    Over72mo = n_tokens_ageNAs_removed - n_tokens_ageOver72mo_removed,
    n_chi_total = n_chi_before_exclusions,
    n_chi_ageNAs = n_chi_ageNAs_removed,
    n_chi_age72over = n_chi_ageOver72mo_removed
  )
```

```{r savingData}
# Save the exclusion data in a file as well as the final data
write_csv(exclusions, "../french/french_data/raw_data/exclusions_french_summary.csv")
write_csv(french_tokens, "../french/french_data/raw_data/french_tokens_excluded.csv")
```

## Coding Speaker Roles

Here we group mothers and fathers together as "parents".

```{r}
# Collapse mothers and fathers into parents
french_tokens$speaker <- "parent"
french_tokens$speaker[french_tokens$speaker_role == "Target_Child"] <- "child"
```

## Coding Age

Here we bin the age data per month.

```{r age}
french_tokens$age <- french_tokens$target_child_age %>% floor()
```

## Grouping Utterance Types

Grouping utterances as declarative, imperative, interrogative, and other.

```{r utterance_types}
# Prepare the utterance_type categories for this study based on the utterance_types in childes-db
## Categories: declarative, imperative, interrogative, and other
french_tokens$utterance_type <-
  recode(french_tokens$utterance_type,
         question = "interrogative",
         `broken for coding` = "other",
         `imperative_emphatic` = "imperative",
         interruption = "other",
         `interruption question` = "interrogative",
         `missing CA terminator` = "other",
         `no break TCU continuation` = "other",
         `question exclamation` = "interrogative",
         `quotation next line` = "other",
         `quotation precedes` = "other",
         `self interruption` = "other",
         `self interruption question` = "interrogative",
         `trail off` = "other",
         `trail off question` = "interrogative"
  )
```

# Defining Negation Words in French

This analysis focuses only on the **negation** category. We start from a
generous candidate set of French negators, then keep the **top 5 most
frequent** in the corpus (computed below).

Preverbal markers (kept separate, not selected from):

* `ne` / `n'` — preverbal negation clitic

Meaning-bearing negators (top 5 selected from these):

* `pas` — postverbal negation ("not")
* `non` — "no"
* `rien` — "nothing"


## Selecting the Negation Words

We count how often each candidate negator occurs in the cleaned token table and
keep the five most frequent. The frequency table is printed so the selection is
transparent.

```{r negation}
negation_markers <- c("ne", "n'")

negation_candidates <- c("pas", "non")

negation_main <- c(negation_markers, negation_candidates)

negation_main
```

## Marking Negation Words

First we mark all words as "nonfunction", then label the top-5 negation words:

```{r FunctionWords}
for (x in negation_main) {
  french_tokens$word[french_tokens$gloss == x] <- x
}
```

## Word Categories

```{r wordcategories}
french_tokens$word_category <- "nonfunction"
french_tokens$word_category[french_tokens$word %in% negation_main]  <- "Negation"
```

Mark function vs. nonfunction:

```{r syncategory}
french_tokens$syncategory <- "Function"
french_tokens$syncategory[french_tokens$word_category == "nonfunction"] <- "nonfunction"
```

## Saving Summary Tables

```{r save_dataframe}
write_feather(french_tokens, "../french/french_data/processed_data/french_tokens_processed.feather")
```
