---
title: "Extracting Function Words of Interest from Childes - Japanese"
author: "Samantha Bai"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(childesr)
library(tidyverse)
library(arrow)
library(stringr)
library(dplyr)
library(knitr)
```

# Loading Data from Childes-DB

We use the package `childesr` to access the data in the CHILDES database. The
code below downloads and stores all utterances by children and parents from the
Japanese collection.

> **Encoding note.** Some CHILDES Japanese corpora transcribe `gloss` in
> romaji (e.g. `nai`, `iya`, `chigau`) rather than Japanese script. Because the
> negator list below is written in Japanese characters (as requested), run the
> diagnostic in the *Inspecting glosses* section first: if the candidate
> negators return zero counts, your corpus is romanized and the candidate list
> needs the romaji forms instead. Everything else in the pipeline is unaffected.

```{r japanese_collection}
target_collection <- "Japanese"
```

```{r directories}
# Create directories
dir.create("../japanese/japanese_data/raw_data", showWarnings = FALSE, recursive = TRUE)
dir.create("../japanese/japanese_data/processed_data", showWarnings = FALSE, recursive = TRUE)
```

```{r ChildesDBimports}
# Define file paths
feather_path <- "../japanese/japanese_data/raw_data/all_japanese_tokens.feather"
csv_path <- "../japanese/japanese_data/raw_data/all_japanese_tokens.csv"

if (file.exists(feather_path)) {
  cat("existing data found\n")
  cat(sprintf("Found existing data file: %s\n", feather_path))
  cat("Loading from saved feather file...\n\n")

  all_japanese_tokens <- arrow::read_feather(feather_path)

} else if (file.exists(csv_path)) {
  cat("existing csv data found\n")
  cat(sprintf("Found existing data file: %s\n", csv_path))
  cat("Loading from CSV file...\n\n")

  all_japanese_tokens <- readr::read_csv(csv_path, show_col_types = FALSE)

  cat("Saving feather version for faster future loading...\n")
  arrow::write_feather(all_japanese_tokens, feather_path)

} else {
  cat("No existing data found - downloading from Childes\n")

  all_japanese_tokens <- get_tokens(
    collection = target_collection,
    role = c("Target_Child", "Mother", "Father"),
    token = "*"
  )

  cat("Saving downloaded data...\n")
  arrow::write_feather(all_japanese_tokens, feather_path)
  readr::write_csv(all_japanese_tokens, csv_path)
}

cat(sprintf("Loaded %d tokens from %d children\n",
            nrow(all_japanese_tokens),
            dplyr::n_distinct(all_japanese_tokens$target_child_id)))
```

# Token Processing

## Exclusions

The following script cleans up the data. Like Mandarin, Japanese has no case
distinction, so no lowercase conversion is needed. We exclude tokens with
missing age and those above 72 months of the child's age. All exclusions are
stored in a file called exclusions_japanese_summary.csv

```{r exclusionsTokens}
# No lowercase conversion needed for Japanese

# Count tokens before exclusions
n_tokens_before_exclusions <- nrow(all_japanese_tokens)

# Number of children before exclusions
n_chi_before_exclusions <-
  all_japanese_tokens$target_child_id %>% unique() %>% length()

japanese_tokens <- all_japanese_tokens

# Removing rows for which age information for the child does not exist
japanese_tokens <-
  japanese_tokens %>% drop_na(target_child_age)

# Count the tokens after removing NA tokens
n_tokens_ageNAs_removed <- nrow(japanese_tokens)

# Number of children after excluding NAs
n_chi_ageNAs_removed <-
  japanese_tokens$target_child_id %>% unique() %>% length()

# Take out data for the age range above 6 years (72 months)
japanese_tokens <-
  japanese_tokens %>%
  filter(target_child_age < 72)

# Count the tokens after excluding older than 6 age range
n_tokens_ageOver72mo_removed <- nrow(japanese_tokens)

# Number of children left after exclusions
n_chi_ageOver72mo_removed <-
  japanese_tokens$target_child_id %>% unique() %>% length()

# Record the dataframe of exclusions
exclusions <-
  data.frame(
    n_tokens_before_exclusions = n_tokens_before_exclusions,
    n_after_ageNAs = n_tokens_ageNAs_removed,
    n_after_age72mo = n_tokens_ageOver72mo_removed,
    missing_age = n_tokens_before_exclusions - n_tokens_ageNAs_removed,
    Over72mo = n_tokens_ageNAs_removed - n_tokens_ageOver72mo_removed,
    n_chi_total = n_chi_before_exclusions,
    n_chi_ageNAs = n_chi_ageNAs_removed,
    n_chi_age72over = n_chi_ageOver72mo_removed
  )
```

```{r savingData}
# Save the exclusion data in a file as well as the final data
write_csv(exclusions, "../japanese/japanese_data/raw_data/exclusions_japanese_summary.csv")
write_csv(japanese_tokens, "../japanese/japanese_data/raw_data/japanese_tokens_excluded.csv")
```

## Coding Speaker Roles

Here we group mothers and fathers together as "parents".

```{r}
# Collapse mothers and fathers into parents
japanese_tokens$speaker <- "parent"
japanese_tokens$speaker[japanese_tokens$speaker_role == "Target_Child"] <- "child"
```

## Coding Age

Here we bin the age data per month.

```{r age}
japanese_tokens$age <- japanese_tokens$target_child_age %>% floor()
```

## Grouping Utterance Types

Grouping utterances as declarative, imperative, interrogative, and other.

```{r utterance_types}
# Prepare the utterance_type categories for this study based on the utterance_types in childes-db
## Categories: declarative, imperative, interrogative, and other
japanese_tokens$utterance_type <-
  recode(japanese_tokens$utterance_type,
         question = "interrogative",
         `broken for coding` = "other",
         `imperative_emphatic` = "imperative",
         interruption = "other",
         `interruption question` = "interrogative",
         `missing CA terminator` = "other",
         `no break TCU continuation` = "other",
         `question exclamation` = "interrogative",
         `quotation next line` = "other",
         `quotation precedes` = "other",
         `self interruption` = "other",
         `self interruption question` = "interrogative",
         `trail off` = "other",
         `trail off question` = "interrogative"
  )
```

# Defining Negation Words in Japanese

This analysis focuses only on the **negation** category. Japanese negation is
largely morphological (the suffix ない / ぬ / ません attaches to verbs and
adjectives), so a gloss-level match mostly captures **standalone** negators,
refusals, and predicate ない. We start from a candidate set written in Japanese
characters, then keep the **top 5 most frequent** in the corpus.

Candidate negators considered (Japanese script):

* ない — "not / there isn't" (predicate negation)
* いいえ — "no" (formal)
* ううん — "no" (informal)
* いけない — "must not"

## Inspecting glosses (encoding check)

```{r inspect_glosses}
# If your corpus is romanized, the Japanese-script candidates will not match.
# This prints the 30 most frequent glosses so you can confirm the script in use.
japanese_tokens %>%
  count(gloss, sort = TRUE) %>%
  slice_head(n = 30) %>%
  knitr::kable(caption = "30 most frequent glosses (script sanity check)")
```

## Selecting the Top 5 Negation Words

We count how often each candidate negator occurs in the cleaned token table and
keep the five most frequent. The frequency table is printed so the selection is
transparent.

```{r negation}
# Candidate negators in Japanese characters (hiragana / katakana / kanji)
negation_candidates <- c(
  "nai",        # ない
  "iya",        # いや / イヤ
  "janai"      # じゃない
)

negation_candidates
```

## Marking Negation Words

First we mark all words as "nonfunction", then label the negation words:

```{r FunctionWords}
for (x in negation_candidates) {
  japanese_tokens$word[japanese_tokens$gloss == x] <- x
}
```

## Word Categories

```{r wordcategories}
japanese_tokens$word_category <- "nonfunction"
japanese_tokens$word_category[japanese_tokens$word %in% negation_candidates] <- "Negation"
```

Mark function vs. nonfunction:

```{r syncategory}
japanese_tokens$syncategory <- "Function"
japanese_tokens$syncategory[japanese_tokens$word_category == "nonfunction"] <- "nonfunction"
```

## Saving Summary Tables

```{r save_dataframe}
write_feather(japanese_tokens, "../japanese/japanese_data/processed_data/japanese_tokens_processed.feather")
```
