---
title: "Extracting Function Words of Interest from Childes - Mandarin"
author: "Samantha Bai"
date: "`r Sys.Date()`"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(childesr)
library(tidyverse)
library(arrow)
library(stringr)
library(dplyr)
```

# Loading Data from Childes-DB

We use the package `childesr` to access the data in the CHILDES database. The code below downloads and stores all utterances by children and parents from Mandarin corpora:

```{r mandarin_corpora}
mandarin_corpora_names <- c(
  "AcadLang",
  "BJCMC",
  "Chang1",
  "Chang2",
  "ChangPlay",
  "ChangPN",
  "Erbaugh",
  "LiReading",
  "LiZhou",
  "NSCtoys",
  "TCCM",
  "TCCM-Reading",
  "Tong",
  "Xinjiang",
  "Zhou1",
  "Zhou2",
  "Zhou3",
  "ZhouAssessment",
  "ZhouDinner",
  "ZhouNarratives"
)
```

```{r directories}
# Create directories
dir.create("../mandarin/mandarin_data/raw_data", showWarnings = FALSE, recursive = TRUE)
dir.create("../mandarin/mandarin_data/processed_data", showWarnings = FALSE, recursive = TRUE)
```

```{r ChildesDBimports}
# Define file paths
feather_path <- "../mandarin/mandarin_data/raw_data/all_mandarin_tokens.feather"
csv_path <- "../mandarin/mandarin_data/raw_data/all_mandarin_tokens.csv"

if (file.exists(feather_path)) {
  cat("EXISTING DATA FOUND\n")
  cat(sprintf("Found existing data file: %s\n", feather_path))
  cat("Loading from saved feather file...\n\n")

  all_mandarin_tokens <- arrow::read_feather(feather_path)

} else if (file.exists(csv_path)) {
  cat("EXISTING CSV DATA FOUND\n")
  cat(sprintf("Found existing data file: %s\n", csv_path))
  cat("Loading from CSV file...\n\n")

  all_mandarin_tokens <- readr::read_csv(csv_path, show_col_types = FALSE)

  cat("Saving feather version for faster future loading...\n")
  arrow::write_feather(all_mandarin_tokens, feather_path)

} else {
  cat("NO EXISTING DATA FOUND - DOWNLOADING FROM CHILDES\n")

  all_mandarin_tokens <- get_tokens(
    corpus = mandarin_corpora_names,
    role = c("Target_Child", "Mother", "Father"),
    token = "*"
  )

  cat("Saving downloaded data...\n")
  arrow::write_feather(all_mandarin_tokens, feather_path)
  readr::write_csv(all_mandarin_tokens, csv_path)
}

cat(sprintf("Loaded %d tokens from %d children\n",
            nrow(all_mandarin_tokens),
            dplyr::n_distinct(all_mandarin_tokens$target_child_id)))
```

# Token Processing

## Exclusions

The following script cleans up the data. Note: no lowercase conversion is needed for Mandarin (no case distinction). We exclude tokens with missing age and those above 72 months of the child's age. All exclusions are stored in a file called exclusions_mandarin_summary.csv

```{r exclusionsTokens}
# No lowercase conversion needed for Mandarin

# Count tokens before exclusions
n_tokens_before_exclusions <- nrow(all_mandarin_tokens)

# Number of children before exclusions
n_chi_before_exclusions <-
  all_mandarin_tokens$target_child_id %>% unique() %>% length()

mandarin_tokens <- all_mandarin_tokens

# Removing rows for which age information for the child does not exist
mandarin_tokens <- 
  mandarin_tokens %>% drop_na(target_child_age)

# Count the tokens after removing NA tokens
n_tokens_ageNAs_removed <- nrow(mandarin_tokens)

# Number of children after excluding NAs
n_chi_ageNAs_removed <-
  mandarin_tokens$target_child_id %>% unique() %>% length()

# Take out data for the age range above 6 years (72 months)
mandarin_tokens <-
  mandarin_tokens %>%
  filter(target_child_age < 72)

# Count the tokens after excluding older than 6 age range
n_tokens_ageOver72mo_removed <- nrow(mandarin_tokens)

# Number of children left after exclusions
n_chi_ageOver72mo_removed <-
  mandarin_tokens$target_child_id %>% unique() %>% length()

# Record the dataframe of exclusions
exclusions <-
  data.frame(
    n_tokens_before_exclusions = n_tokens_before_exclusions,
    n_after_ageNAs = n_tokens_ageNAs_removed,
    n_after_age72mo = n_tokens_ageOver72mo_removed,
    missing_age = n_tokens_before_exclusions - n_tokens_ageNAs_removed,
    Over72mo = n_tokens_ageNAs_removed - n_tokens_ageOver72mo_removed,
    n_chi_total = n_chi_before_exclusions,
    n_chi_ageNAs = n_chi_ageNAs_removed,
    n_chi_age72over = n_chi_ageOver72mo_removed
  )
```

```{r savingData}
# Save the exclusion data in a file as well as the final data
write_csv(exclusions, "../mandarin/mandarin_data/raw_data/exclusions_mandarin_summary.csv")
write_csv(mandarin_tokens, "../mandarin/mandarin_data/raw_data/mandarin_tokens_excluded.csv")
```

## Coding Speaker Roles

Here we group mothers and fathers together as "parents".

```{r}
# Collapse mothers and fathers into parents
mandarin_tokens$speaker[mandarin_tokens$speaker_role] <- "parent" #only mother and father
mandarin_tokens$speaker[mandarin_tokens$speaker_role == "Target_Child"] <- "child"
```

## Coding Age

Here we bin the age data per month.

```{r age}
mandarin_tokens$age <- mandarin_tokens$target_child_age %>% floor()
```

## Grouping Utterance Types

Grouping utterances as declarative, imperative, interrogative, and other.

```{r utterance_types}
# Prepare the utterance_type categories for this study based on the utterance_types in childes-db
## Categories: declarative, imperative, interrogative, and other
mandarin_tokens$utterance_type <-
  recode(mandarin_tokens$utterance_type, 
         question = "interrogative",
         `broken for coding` = "other",
         `imperative_emphatic` = "imperative",
         interruption = "other",
         `interruption question` = "interrogative",
         `missing CA terminator` = "other",
         `no break TCU continuation` = "other",
         `question exclamation` = "interrogative",
         `quotation next line` = "other",
         `quotation precedes` = "other",
         `self interruption` = "other",
         `self interruption question` = "interrogative",
         `trail off` = "other",
         `trail off question` = "interrogative"
  )
```

# Defining Function Words in Mandarin

Note: Mandarin does not have contractions like English, so we do not need a separate contracted token processing pipeline. We work directly with `mandarin_tokens`.

This analysis focuses on four core logical word categories in Mandarin:

* Negation (no/not): 不 (bù, general negation), 没 (méi, negation of have/completion), 没有 (méiyǒu, negation of have/completion), 别 (bié, prohibitive negation / "don't")
* Conjunction (and): 和 (hé), 跟 (gēn), 而且 (érqiě, "and also/moreover")
* Disjunction (or): 或 (huò), 或者 (huòzhě), 还是 (háishi, "or" in questions)
* Conditionals (if): 如果 (rúguǒ), 要是 (yàoshi, colloquial "if"),

## Defining previous and after words

```{r betweenwords}
# Define the word before and after the target function word
mandarin_tokens <- mandarin_tokens %>%
  arrange(utterance_id, token_order) %>%
  group_by(utterance_id) %>%
  mutate(
    prev_gloss = lag(gloss),
    next_gloss = lead(gloss),
    prev_pos   = lag(part_of_speech),
    next_pos   = lead(part_of_speech)
  ) %>%
  ungroup()

mandarin_tokens$word <- "nonfunction"
```

## Marking Function Words

First we mark all words as "nonfunction", then label the function words of interest:

```{r FunctionWords}

function_words <- c(
  # Negation (no/not)
  "不", "没", "没有", "别",
  # Conjunction (and)
  "和", "而且",
  # Disjunction (or)
  "或者",
  # Conditionals (if)
  "如果", "要是", "的话"
)

for (x in function_words) {
  mandarin_tokens$word[mandarin_tokens$gloss == x] <- x
}

# Only mark 还是 when it occurs in an interrogative utterance (the "or" sense).
# In declarative/imperative utterances, 还是 means "still/preferably."
mandarin_tokens$word[
  mandarin_tokens$gloss == "还是" &
  mandarin_tokens$utterance_type == "interrogative"
] <- "还是"

# Only mark 跟 when it is likely used as a conjunction ("and"),
# i.e., flanked by nominal-type elements (nouns or pronouns) on both sides.
mandarin_tokens$word[
  mandarin_tokens$gloss == "跟" &
  str_detect(mandarin_tokens$prev_pos, "^(n|pro)") &
  str_detect(mandarin_tokens$next_pos, "^(n|pro)")
] <- "跟"
```

## Word Categories

```{r wordcategories}
mandarin_tokens$word_category <- "nonfunction"

mandarin_tokens$word_category[mandarin_tokens$word %in% c("不", "没", "没有", "别")] <- "Negation"
mandarin_tokens$word_category[mandarin_tokens$word %in% c("和", "跟", "而且")] <- "Conjunction"
mandarin_tokens$word_category[mandarin_tokens$word %in% c("或者", "还是")] <- "Disjunction"
mandarin_tokens$word_category[mandarin_tokens$word %in% c("如果", "要是", "的话")] <- "Conditionals"
```

Mark function vs. nonfunction:

```{r syncategory}
mandarin_tokens$syncategory <- "Function"
mandarin_tokens$syncategory[mandarin_tokens$word_category == "nonfunction"] <- "nonfunction"
```

## Saving Summary Tables

```{r save_dataframe}
write_feather(mandarin_tokens, "../mandarin/mandarin_data/processed_data/mandarin_tokens_processed.feather")
```


```{r query}
tokens <- read_feather("mandarin_tokens_processed.feather")

child_haishi <- tokens %>%
  filter(speaker_role == "Target_Child", gloss == "还是") %>%
  select(target_child_name, target_child_age, utterance_id, transcript_id)

# Then to see the surrounding utterance, group tokens by utterance_id
child_haishi_utts <- tokens %>%
  filter(utterance_id %in% child_haishi$utterance_id) %>%
  arrange(utterance_id, token_order) %>%
  group_by(utterance_id, speaker_role, target_child_age) %>%
  summarise(utterance = paste(gloss, collapse = ""), .groups = "drop")

print(child_haishi_utts, n = 30)
```