---
title: "Mandarin Plots and Curves"
author: "Samantha Bai"
date: "`r Sys.Date()`"
output: pdf_document
---

# Abstract



# Setup
This section loads the R packages needed for data processing, modeling, and visualization. These libraries support reading the processed data file, working with tidy data, fitting Bayesian growth curve models, and arranging the final plots.

```{r packages, include=FALSE}
library(tidyverse)
library(arrow) 
library(brms)
library(ggeffects) 
library(ggrepel)
library(grid) 
library(gridExtra)
```

```{r}
knitr::opts_chunk$set(error = TRUE)
```

# Load Data
This section loads the processed Mandarin token data. The dataset is organized at the token level and includes information such as speaker, age, word form, and grammatical category. This dataset serves as the starting point for the frequency tables, plots, and growth curve models.

```{r processedMandarinTokens}
# Create directories if they don't exist
dir.create("../mandarin/mandarin_model/modeling", showWarnings = FALSE, recursive = TRUE)
dir.create("../mandarin/mandarin_data/processed_data", showWarnings = FALSE, recursive = TRUE)

mandarin_tokens_processed <- read_feather("../mandarin/mandarin_data/processed_data/mandarin_tokens_processed.feather")
```

# Computing Cumulative Relative Frequencies

This section computes cumulative relative frequencies for the Mandarin tokens. Because naturalistic child language data can be noisy from month to month, the analysis uses cumulative counts across age. This makes the developmental patterns smoother and easier to model. The resulting frequency tables provide the foundation for the later plots and growth curve analyses.

## Function vs. Content Words

This section calculates the cumulative relative frequency of function words and content words separately for children and caregivers. The goal is to examine how the proportion of function word use changes across age. This broad comparison gives an overall view of grammatical development before looking at individual function words in more detail.

```{r}
syncategory_relfreq <-
  mandarin_tokens_processed %>%
  group_by(syncategory, speaker, age) %>%
  summarise(freq = n(), .groups = "drop") %>%
  complete( 
    nesting(syncategory)  %>% mutate(speaker = "child"),
    age = 0:10,
    fill = list(freq = 0)
  ) %>%
  mutate(freq = ifelse(speaker == "child" & age <= 10, 0, freq)) %>%
  group_by(speaker, age) %>%
  mutate(total=sum(freq), relfreq = ifelse(total == 0, 0, freq / total), pct=relfreq*100) %>%
  group_by(syncategory, speaker) %>%
  arrange(age) %>%
  mutate(cum_freq = cumsum(freq), cum_total= cumsum(total), cumulative_relfreq = cumsum(freq)/cumsum(total), cumulative_pct=cumulative_relfreq*100)

saveRDS(syncategory_relfreq, "syncategory_relfreq.RDS")
```

## Individual Function Words

This section calculates cumulative relative frequencies for each individual function word. The data are grouped by word, speaker, and age, allowing us to trace how each function word changes over developmental time. These results are later used to fit word specific growth curves and estimate when each word begins to appear productively in child speech.

```{r}
functionword_relfreq <-
  mandarin_tokens_processed %>%
  group_by(word, speaker, age) %>%
  summarise(freq = n(), .groups = "drop") %>%
  complete(
    nesting(word) %>% mutate(speaker = "child"), 
    age = 0:10,
    fill = list(freq = 0)
  ) %>%
  mutate(freq = ifelse(speaker == "child" & age <= 10, 0, freq)) %>% # zero numerator for early ages
  group_by(speaker, age) %>%
  mutate(total=sum(freq), relfreq = ifelse(total == 0, 0, freq / total), ppt=relfreq*1000) %>%
  group_by(word, speaker) %>%
  arrange(age) %>%
  mutate(cum_freq = cumsum(freq), cum_total= cumsum(total), cumulative_relfreq = ifelse(cum_total == 0, 0, cum_freq / cum_total), cumulative_ppt=cumulative_relfreq*1000)

saveRDS(functionword_relfreq, "functionword_relfreq.RDS")
```

## Function Word Semantic Categories

This section calculates cumulative relative frequencies by semantic category, such as negation, conjunction, disjunction, and conditionals. This provides an intermediate level of analysis between the broad function word category and individual lexical items.

```{r}
wordcategory_relfreq <-
  mandarin_tokens_processed %>%
  group_by(word_category, speaker, age) %>%
  summarise(freq = n(), .groups = "drop") %>%
  complete(
    nesting(word_category)  %>% mutate(speaker = "child"),
    age = 0:10,
    fill = list(freq = 0)
  ) %>%
  mutate(freq = ifelse(speaker == "child" & age <= 10, 0, freq)) %>% 
  group_by(speaker, age) %>%
  mutate(total=sum(freq), relfreq = ifelse(total == 0, 0, freq / total), ppt=relfreq*1000) %>%
  group_by(word_category, speaker) %>%
  arrange(age) %>%
  mutate(cum_freq = cumsum(freq), cum_total= cumsum(total), cumulative_relfreq = ifelse(cum_total == 0, 0, cum_freq / cum_total))

saveRDS(wordcategory_relfreq, "wordcategory_relfreq.RDS")
```

# Plots and Growth Curves

This section moves from descriptive frequency calculations to growth curve modeling. The goal is to summarize each developmental trajectory with a small set of interpretable model parameters. The plots show the observed frequency patterns across age, while the fitted curves estimate the underlying developmental trend.

## Content vs. Function Word Production

This section visualizes the overall percentage of function word use across age for both children and caregivers. It then fits a Bayesian growth curve model to the child function word trajectory. The fitted curve is plotted together with the observed data, allowing us to evaluate how well the model captures the developmental increase in function word production.

```{r}
function_words_plot <-
  syncategory_relfreq %>%
  filter(syncategory=="Function") %>%
  ggplot(aes(age, pct)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() +
  xlab("Age (Months)") + ylab("Percentage") + 
  scale_y_continuous(limits = c(0, 100)) +
  theme(text = element_text(size = 14))
```

```{r function_words_growth_model, include=FALSE}
function_words_lagModel <- brm(
  bf(pct  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(syncategory_relfreq, syncategory=="Function", speaker=="child"),
  prior = c(
    prior(uniform(0, 100), nlpar = "upperAsymptote", lb = 0, ub = 100),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 0, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/mandarin_function_word_lagModel",
  iter = 10000)
```

```{r function_word_predictions}
function_words_predictions <- as.data.frame(fitted(function_words_lagModel))

function_words_childdata <- filter(syncategory_relfreq, syncategory=="Function", speaker=="child")
function_words_childdata$predictions <- function_words_predictions[, "Estimate"]

saveRDS(function_words_childdata, "../mandarin/mandarin_data/processed_data/mandarin_function_words_childdata.RDS")
```

```{r function_words_prediction_plot} 
function_words_plot <-
  ggplot(function_words_childdata, aes(x = age, y = pct)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="Function Words", x="Child Age (Month)", y="Percent") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```


## Distribution of Individual Function Words

This section applies the same modeling procedure to each individual function word. For each word, the code first plots the observed cumulative frequency trajectory, then fits a Bayesian growth curve model to the child data, extracts the fitted values, and creates an overlay plot comparing the observed and fitted values. The estimated lag parameter is also saved as an estimate of the word’s age of production. The words are organized by semantic category to make the developmental patterns easier to compare.

### Negation

This section analyzes Mandarin negation words, including 不bù, 没méi, 没有méiyǒu, and 别bié. For each word, the code plots its cumulative frequency over age, fits a growth curve to the child production data, and extracts the estimated age of production. These words allow us to compare different types of negation, such as general negation, negation of possession or completion, and prohibitive negation.

##### 不 bù (general negation)

This subsection analyzes the developmental trajectory of 不 bù, a general negation marker in Mandarin. It is commonly used to negate actions, states, or qualities, similar to “not” in English. The code visualizes its cumulative use across age, fits the growth curve model, and adds the estimated age of production to the summary table.

```{r bu_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="不") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("不 bù") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```


```{r bu_growth_model, include=FALSE}
bu_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="不", speaker=="child"),
  prior = c(
    prior(uniform(0, 40), nlpar = "upperAsymptote", lb = 0, ub = 40),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/bu_lagModel",
  iter = 10000)
```

```{r bu_predictions}
bu_predictions <- as.data.frame(fitted(bu_lagModel))

bu_childdata <- filter(functionword_relfreq, word=="不", speaker=="child")
bu_childdata$predictions <- bu_predictions[, "Estimate"]

saveRDS(bu_childdata, "../mandarin/mandarin_data/processed_data/bu_childdata.RDS")
```

```{r bu_age_of_production}
age_of_production <- 
  data.frame(word = c("不 bù"), 
           Estimate = c(round(fixef(bu_lagModel)[3,1],1)),
           Est.Error = c(round(fixef(bu_lagModel)[3,2],1)),
           Q2.5 = c(round(fixef(bu_lagModel)[3,3],1)),
           Q97.5 = c(round(fixef(bu_lagModel)[3,4],1))
           )
```

```{r bu_prediction_plot} 
bu_plot <-
  ggplot(bu_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="不 bù", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

##### 没 méi (negation of have/completion)

This subsection analyzes the developmental trajectory of 没 méi, a negation word often used to express “not have,” “there is not,” or that an action has not occurred. The code plots its cumulative frequency, fits the growth curve model, and adds its estimated age of production to the summary table.

```{r mei_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="没") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("没 méi") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r mei_growth_model, include=FALSE}
mei_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="没", speaker=="child"),
  prior = c(
    prior(uniform(0, 20), nlpar = "upperAsymptote", lb = 0, ub = 20),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/mei_lagModel",
  iter = 10000)
```

```{r mei_predictions}
mei_predictions <- as.data.frame(fitted(mei_lagModel))

mei_childdata <- filter(functionword_relfreq, word=="没", speaker=="child")
mei_childdata$predictions <- mei_predictions[, "Estimate"]

saveRDS(mei_childdata, "../mandarin/mandarin_data/processed_data/mei_childdata.RDS")
```

```{r mei_prediction_plot} 
mei_plot <-
  ggplot(mei_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="没 méi", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r mei_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "没 méi",
             Estimate  = round(fixef(mei_lagModel)[3, 1], 1),
             Est.Error = round(fixef(mei_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(mei_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(mei_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

##### 没有 méiyǒu (negation of have/completion)

This subsection analyzes 没有 méiyǒu, a fuller negation form meaning “do not have” or “have not.” It is commonly used to negate possession, existence, or completed actions. The code follows the same procedure by plotting the observed developmental pattern, fitting the growth curve, saving predictions, and recording the estimated age of production.

```{r meiyou_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="没有") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("没有 méiyǒu") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r meiyou_growth_model, include=FALSE}
meiyou_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="没有", speaker=="child"),
  prior = c(
    prior(uniform(0, 20), nlpar = "upperAsymptote", lb = 0, ub = 20),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/meiyou_lagModel",
  iter = 10000)
```

```{r meiyou_predictions}
meiyou_predictions <- as.data.frame(fitted(meiyou_lagModel))

meiyou_childdata <- filter(functionword_relfreq, word=="没有", speaker=="child")
meiyou_childdata$predictions <- meiyou_predictions[, "Estimate"]

saveRDS(meiyou_childdata, "../mandarin/mandarin_data/processed_data/meiyou_childdata.RDS")
```

```{r meiyou_prediction_plot} 
meiyou_plot <-
  ggplot(meiyou_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="没有 méiyǒu", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r meiyou_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "没有 méiyǒu",
             Estimate  = round(fixef(meiyou_lagModel)[3, 1], 1),
             Est.Error = round(fixef(meiyou_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(meiyou_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(meiyou_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

##### 别 bié (prohibitive negation / "don't")

This subsection analyzes 别 bié, a prohibitive negation marker meaning “do not” or “don’t.” It is usually used to tell someone not to do something. The code estimates how this word appears over developmental time and adds its model-based age of production to the larger comparison table.

```{r bie_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="别") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("别 bié") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r bie_growth_model, include=FALSE}
bie_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="别", speaker=="child"),
  prior = c(
    prior(uniform(0, 10), nlpar = "upperAsymptote", lb = 0, ub = 10),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/bie_lagModel",
  iter = 10000)
```

```{r bie_predictions}
bie_predictions <- as.data.frame(fitted(bie_lagModel))

bie_childdata <- filter(functionword_relfreq, word=="别", speaker=="child")
bie_childdata$predictions <- bie_predictions[, "Estimate"]

saveRDS(bie_childdata, "../mandarin/mandarin_data/processed_data/bie_childdata.RDS")
```

```{r bie_prediction_plot} 
bie_plot <-
  ggplot(bie_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="别 bié", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r bie_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "别 bié",
             Estimate  = round(fixef(bie_lagModel)[3, 1], 1),
             Est.Error = round(fixef(bie_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(bie_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(bie_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

### Conjunction

This section analyzes Mandarin conjunction words, including 和hé, 跟gēn, and 而且érqiě. These words are used to connect nouns, phrases, or clauses. For each word, the code plots the cumulative developmental trajectory, fits a growth curve to child production, and saves the estimated age of production.

##### 和 hé

This subsection analyzes 和 hé, a common Mandarin conjunction meaning “and.” It is mainly used to connect nouns, people, or noun phrases. The code visualizes its cumulative frequency across age, fits the growth curve model, and adds the estimated age of production to the summary table.

```{r he_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="和") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("和 hé") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r he_growth_model, include=FALSE}
he_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="和", speaker=="child"),
  prior = c(
    prior(uniform(0, 10), nlpar = "upperAsymptote", lb = 0, ub = 10),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/he_lagModel",
  iter = 10000)
```

```{r he_predictions}
he_predictions <- as.data.frame(fitted(he_lagModel))

he_childdata <- filter(functionword_relfreq, word=="和", speaker=="child")
he_childdata$predictions <- he_predictions[, "Estimate"]

saveRDS(he_childdata, "../mandarin/mandarin_data/processed_data/he_childdata.RDS")
```

```{r he_prediction_plot} 
he_plot <-
  ggplot(he_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="和 hé", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r he_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "和 hé",
             Estimate  = round(fixef(he_lagModel)[3, 1], 1),
             Est.Error = round(fixef(he_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(he_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(he_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

##### 跟 gēn

This subsection analyzes 跟 gēn, which can mean “with” or function as a conjunction meaning “and” in some contexts. In this analysis, it is treated as a conjunction when it connects noun-like elements. The code plots its cumulative use, fits the child growth curve, saves predicted values, and records the estimated age of production.

```{r gen_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="跟") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("跟 gēn") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r gen_growth_model, include=FALSE}
gen_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="跟", speaker=="child"),
  prior = c(
    prior(uniform(0, 10), nlpar = "upperAsymptote", lb = 0, ub = 10),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/gen_lagModel",
  iter = 10000)
```

```{r gen_predictions}
gen_predictions <- as.data.frame(fitted(gen_lagModel))

gen_childdata <- filter(functionword_relfreq, word=="跟", speaker=="child")
gen_childdata$predictions <- gen_predictions[, "Estimate"]

saveRDS(gen_childdata, "../mandarin/mandarin_data/processed_data/gen_childdata.RDS")
```

```{r gen_prediction_plot} 
gen_plot <-
  ggplot(gen_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="跟 gēn", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r gen_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "跟 gēn",
             Estimate  = round(fixef(gen_lagModel)[3, 1], 1),
             Est.Error = round(fixef(gen_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(gen_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(gen_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```


##### 而且 érqiě ("and also/moreover")

##not enough data

This subsection analyzes 而且 érqiě, a conjunction meaning “and also,” “moreover,” or “in addition.” It is often used to connect clauses or add extra information. Because this is a more complex connective, the model helps estimate when it begins to emerge in child speech relative to simpler conjunctions.

```{r erqie_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="而且") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("而且 érqiě") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r erqie_growth_model, include=FALSE}
erqie_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="而且", speaker=="child"),
  prior = c(
    prior(uniform(0, 5), nlpar = "upperAsymptote", lb = 0, ub = 5),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/erqie_lagModel",
  iter = 10000)
```

```{r erqie_predictions}
erqie_predictions <- as.data.frame(fitted(erqie_lagModel))

erqie_childdata <- filter(functionword_relfreq, word=="而且", speaker=="child")
erqie_childdata$predictions <- erqie_predictions[, "Estimate"]

saveRDS(erqie_childdata, "../mandarin/mandarin_data/processed_data/erqie_childdata.RDS")
```

```{r erqie_prediction_plot} 
erqie_plot <-
  ggplot(erqie_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="而且 érqiě", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r erqie_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "而且 érqiě",
             Estimate  = round(fixef(erqie_lagModel)[3, 1], 1),
             Est.Error = round(fixef(erqie_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(erqie_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(erqie_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```


### Disjunction

This section analyzes Mandarin disjunction words, including 或者huòzhě and 还是háishi. These words express alternatives, but they are used in different contexts. The code compares their developmental trajectories by plotting cumulative frequency, fitting growth curves, and estimating age of production.

##### 或者 huòzhě

This subsection analyzes 或者 huòzhě, a Mandarin disjunction marker meaning “or.” It is usually used to present alternatives in statements or choices. The code visualizes its cumulative use, fits a growth curve to the child data, and records its estimated age of production.

Example:


```{r huozhe_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="或者") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("或者 huòzhě") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r huozhe_growth_model, include=FALSE}
huozhe_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="或者", speaker=="child"),
  prior = c(
    prior(uniform(0, 2), nlpar = "upperAsymptote", lb = 0, ub = 2),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/huozhe_lagModel",
  iter = 10000)
```

```{r huozhe_predictions}
huozhe_predictions <- as.data.frame(fitted(huozhe_lagModel))

huozhe_childdata <- filter(functionword_relfreq, word=="或者", speaker=="child")
huozhe_childdata$predictions <- huozhe_predictions[, "Estimate"]

saveRDS(huozhe_childdata, "../mandarin/mandarin_data/processed_data/huozhe_childdata.RDS")
```

```{r huozhe_prediction_plot} 
huozhe_plot <-
  ggplot(huozhe_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="或者 huòzhě", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r huozhe_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "或者 huòzhě",
             Estimate  = round(fixef(huozhe_lagModel)[3, 1], 1),
             Est.Error = round(fixef(huozhe_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(huozhe_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(huozhe_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

##### 还是 háishi ("or" in questions)

This subsection analyzes 还是 háishi, a disjunction word meaning “or,” especially in questions. It is commonly used when asking someone to choose between alternatives. The code estimates its developmental trajectory and allows comparison with 或者, which is used in a different disjunctive context.

example:
是开心还是害怕?
Is (he/she) happy or scared?

```{r haishi_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="还是") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("还是 háishi") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r haishi_growth_model, include=FALSE}
haishi_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="还是", speaker=="child"),
  prior = c(
    prior(uniform(0, 5), nlpar = "upperAsymptote", lb = 0, ub = 5),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/haishi_lagModel",
  iter = 10000)
```

```{r haishi_predictions}
haishi_predictions <- as.data.frame(fitted(haishi_lagModel))

haishi_childdata <- filter(functionword_relfreq, word=="还是", speaker=="child")
haishi_childdata$predictions <- haishi_predictions[, "Estimate"]

saveRDS(haishi_childdata, "../mandarin/mandarin_data/processed_data/haishi_childdata.RDS")
```

```{r haishi_prediction_plot} 
haishi_plot <-
  ggplot(haishi_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="还是 háishi", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r haishi_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "还是 háishi",
             Estimate  = round(fixef(haishi_lagModel)[3, 1], 1),
             Est.Error = round(fixef(haishi_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(haishi_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(haishi_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

### Conditionals

This section analyzes Mandarin conditional expressions, including 如果rúguǒ, 要是yàoshi, and 的话dehuà. These words and phrases are related to conditional meaning, such as “if” or “if that is the case.” The code plots each word’s developmental trajectory, fits a growth curve model, and estimates when each form enters productive child speech.

##### 如果 rúguǒ

This subsection analyzes 如果 rúguǒ, a conditional marker meaning “if.” It is often used to introduce a hypothetical condition or situation. Because this word appears later and less frequently, the model is fit to child data from later ages. The code plots the observed pattern, fits the growth curve, and records the estimated age of production.

example:

如果下雨天……
If (it’s) a rainy day …

```{r ruguo_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="如果") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("如果 rúguǒ") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r ruguo_growth_model, include=FALSE}
ruguo_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="如果", speaker=="child"),
  prior = c(
    prior(uniform(0, 2), nlpar = "upperAsymptote", lb = 0, ub = 2),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/ruguo_lagModel",
  iter = 10000)
```

```{r ruguo_predictions}
ruguo_predictions <- as.data.frame(fitted(ruguo_lagModel))

ruguo_childdata <- filter(functionword_relfreq, word=="如果", speaker=="child")
ruguo_childdata$predictions <- ruguo_predictions[, "Estimate"]

saveRDS(ruguo_childdata, "../mandarin/mandarin_data/processed_data/ruguo_childdata.RDS")
```

```{r ruguo_prediction_plot} 
ruguo_plot <-
  ggplot(ruguo_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="如果 rúguǒ", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r ruguo_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "如果 rúguǒ",
             Estimate  = round(fixef(ruguo_lagModel)[3, 1], 1),
             Est.Error = round(fixef(ruguo_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(ruguo_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(ruguo_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```

##### 要是 yàoshi (colloquial "if")

This subsection analyzes 要是 yàoshi, a more colloquial conditional marker also meaning “if.” It is used to introduce a possible or imagined condition, often in everyday speech. The code estimates its developmental trajectory and compares its emergence with other conditional forms.

example:
所以要是有别人在……
So if there are other people around …


```{r yaoshi_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="要是") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("要是 yàoshi") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r yaoshi_growth_model, include=FALSE}
yaoshi_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="要是", speaker=="child"),
  prior = c(
    prior(uniform(0, 2), nlpar = "upperAsymptote", lb = 0, ub = 2),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/yaoshi_lagModel",
  iter = 10000)
```

```{r yaoshi_predictions}
yaoshi_predictions <- as.data.frame(fitted(yaoshi_lagModel))

yaoshi_childdata <- filter(functionword_relfreq, word=="要是", speaker=="child")
yaoshi_childdata$predictions <- yaoshi_predictions[, "Estimate"]

saveRDS(yaoshi_childdata, "../mandarin/mandarin_data/processed_data/yaoshi_childdata.RDS")
```

```{r yaoshi_prediction_plot} 
yaoshi_plot <-
  ggplot(yaoshi_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="要是 yàoshi", x="Child Age (Month)", y="Parts per Thousand") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r yaoshi_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "要是 yàoshi",
             Estimate  = round(fixef(yaoshi_lagModel)[3, 1], 1),
             Est.Error = round(fixef(yaoshi_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(yaoshi_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(yaoshi_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```


##### 的话 dehuà

This subsection analyzes 的话 dehuà, a conditional phrase often used at the end of a clause, roughly meaning “if that is the case” or “if.” It usually works together with a condition stated earlier in the sentence. The code plots its cumulative frequency, fits the growth curve model, and adds its estimated age of production to the summary table.

example:
木头的话它……
If it’s wood, it (would) …


```{r dehua_plot, echo=FALSE}
functionword_relfreq %>%
  filter(word=="的话") %>%
  ggplot(aes(age, cumulative_ppt)) +
  geom_point() +
  facet_grid(.~speaker) +
  theme_bw() + 
  ggtitle("的话 dehuà") +
  xlab("Age (Months)") + ylab("Cumulative Parts Per Thousand")
```

```{r dehua_growth_model, include=FALSE}
dehua_lagModel <- brm(
  bf(cumulative_ppt  ~ upperAsymptote * exp(-exp(((growthRate*exp(1))/upperAsymptote)*(lag-age)+1)),
     upperAsymptote ~ 1,
     growthRate ~ 1,
     lag ~ 1,
     nl = TRUE),
  data = filter(functionword_relfreq, word=="的话", speaker=="child"),
  prior = c(
    prior(uniform(0, 2), nlpar = "upperAsymptote", lb = 0, ub = 2),
    prior(uniform(0, 10), nlpar = "growthRate", lb = 0, ub = 10),
    prior(uniform(10, 72), nlpar = "lag", lb = 10, ub = 72)
  ),
  file = "../mandarin/mandarin_model/modeling/dehua_lagModel",
  iter = 10000)
```

```{r dehua_predictions}
dehua_predictions <- as.data.frame(fitted(dehua_lagModel))

dehua_childdata <- filter(functionword_relfreq, word=="的话", speaker=="child")
dehua_childdata$predictions <- dehua_predictions[, "Estimate"]

saveRDS(dehua_childdata, "../mandarin/mandarin_data/processed_data/dehua_childdata.RDS")
```

```{r dehua_prediction_plot} 
dehua_plot <-
  ggplot(dehua_childdata, aes(x = age, y = cumulative_ppt)) +
  geom_point(aes(color = "Actual Data"), size = 2) +
  geom_line(aes(y = predictions, color = "Fitted Values"), size = 1) +
  scale_color_manual(name = "Legend", values = c("Actual Data" = "black", "Fitted Values" = "blue")) +
  theme_bw() + labs(title="的话 dehuà", x="", y="") + 
  theme(legend.position = "none") +   
  theme(
    plot.title = element_text(size = 20, hjust = 0.5),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    axis.text.x = element_text(size = 14),
    axis.text.y = element_text(size = 14),
    legend.title = element_text(size = 14),
    legend.text  = element_text(size = 12)
  )
```

```{r dehua_age_of_production}
age_of_production <- bind_rows(
  age_of_production,
  data.frame(word      = "的话 dehuà",
             Estimate  = round(fixef(dehua_lagModel)[3, 1], 1),
             Est.Error = round(fixef(dehua_lagModel)[3, 2], 1),
             Q2.5      = round(fixef(dehua_lagModel)[3, 3], 1),
             Q97.5     = round(fixef(dehua_lagModel)[3, 4], 1),
             stringsAsFactors = FALSE)
)
```


# Collection of some plots

This section assembles the individual fitted-curve plots into themed multi-panel figures. Arranging conceptually related words side by side allows the reader to visually compare acquisition trajectories within a semantic class, which is more informative than inspecting each fit in isolation.
```{r}
library(gridExtra)

grid.arrange(bu_plot, mei_plot, meiyou_plot, bie_plot,
             layout_matrix = rbind(c(1, 2), c(3, 4)),
             bottom = textGrob("Age (Months)", gp = gpar(fontsize = 13)),
             left   = textGrob("Words (Per Thousand)", gp = gpar(fontsize = 13), rot = 90))

grid.arrange(he_plot, gen_plot, erqie_plot,
             layout_matrix = rbind(c(1, 2), c(3, 4)),
             bottom = textGrob("Age (Months)", gp = gpar(fontsize = 13)),
             left   = textGrob("Words (Per Thousand)", gp = gpar(fontsize = 13), rot = 90))

grid.arrange(huozhe_plot, haishi_plot,
             layout_matrix = rbind(c(1, 2), c(3, 4)),
             bottom = textGrob("Age (Months)", gp = gpar(fontsize = 13)),
             left   = textGrob("Words (Per Thousand)", gp = gpar(fontsize = 13), rot = 90))

grid.arrange(ruguo_plot, yaoshi_plot, dehua_plot,
             layout_matrix = rbind(c(1, 2), c(3, 4)),
             bottom = textGrob("Age (Months)", gp = gpar(fontsize = 13)),
             left   = textGrob("Words (Per Thousand)", gp = gpar(fontsize = 13), rot = 90))
```

# Age of Production Plot

This concluding section synthesizes the lag-parameter estimates accumulated across all individual word models into a single summary visualization. The resulting figure provides, on a single panel, an estimated developmental ordering of the analyzed function words together with a graphical representation of the uncertainty associated with each estimate. This visualization constitutes the principal empirical contribution of the document, condensing the entire word-by-word modeling effort into a single comparative display of when, on average and with what uncertainty, each function word enters productive child speech.

```{r}
age_of_production <- 
  age_of_production %>%
  mutate(word = fct_reorder(word, Estimate))

saveRDS(age_of_production, "../mandarin/mandarin_data/processed_data/mandarin_age_of_production.RDS")
```

```{r}
age_of_production <- readRDS("../mandarin/mandarin_data/processed_data/mandarin_age_of_production.RDS")

functionword_onsetage_plot <-
  age_of_production %>%
  mutate(word = fct_reorder(word, Estimate)) %>%
  ggplot(aes(x=Estimate, y=word)) +
  geom_pointrange(aes(xmin = Q2.5, xmax = Q97.5)) +
  theme_bw() + 
  theme(axis.text.y = element_text(size = 12), xlab="age") +
  scale_x_continuous(breaks = seq(0, 72, by = 3)) +
  labs(x = "Age (Months)", y="") +
  theme(text = element_text(size = 12))
```
